---
title: "Lab5_NotTeamOne"
author: "David Orozco, Anderson Mun, Arie del Valle, Ethan Schacht, Ryan Tate"
date: "February 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
milk <- read.csv('state_milk_production.csv')
head(milk)
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
```
****
## Team Component
****
### Team Graph
****
```{r, echo=FALSE}

milksub <- milk %>%
  filter(state %in% c('Texas','Colorado','Connecticut', 'Alaska', 'California')) %>%
  select(state, year, milk_million)

ggplot(data = milksub, aes(x = year, y = milk_million, color = state)) +
  geom_boxplot() + 
  ggtitle('Milk Produced over time by State') +
  xlab('Year') +
  ylab('Milk Produced (Million lbs.)')

```

 * DO THIS -> After everyone is finished, as a team, write a few sentences in the team report in R Markdown detailing what you found to be the most helpful in learning about this data. 
 
```{r, echo=FALSE} 
minyear <- milk %>% 
  group_by(year) %>% 
  summarize(total = sum(milk_million, na.rm=TRUE)) %>% 
 top_n(-1,total) 
minyear 
```

* 1975 is the year when the least milk was produced in the United States

```{r, echo=FALSE} 
 
mostyear <- milk %>% 
  group_by(year) %>% 
  summarize(total = sum(milk_million, na.rm=TRUE)) %>% 
   top_n(1,total)
mostyear 
  
```

* 2017 is the year when the most milk was produced in the United States


```{r, echo=FALSE} 

five_least_states <- milk %>% 
  filter(year == 2017) %>% 
    top_n(-5,milk_million) %>% arrange(milk_million)

five_least_states 
```

* In 2017, the 5 states that produced the least milk were Alaska, Rhode Island, Hawaii, Arkansas, and Alabama in that order


```{r, echo=FALSE}
 
five_most_states <- milk %>% 
  filter(year == 2017) %>% 
 top_n(5,milk_million) %>% arrange(desc(milk_million))
   
five_most_states 
``` 

* In 2017, the 5 states that produced the most milk were Californaia Wisconsin, New York, Idaho and Texas in that order. 

### Individual Component
****
#### Arie's Data
****
```{r, echo=FALSE}

milk1996 <- milk %>% filter(year == 1996) 
ggplot(data = milk1996 , mapping = aes(x = milk_million ))+
  geom_density()+
  ggtitle('Distribution of Milk Production in 1996')+
  xlab('Milk Produced(Millions lbs.)')+
  ylab('Density')

```

* The mean and median millions of pounds of milk are 3080.12 and 1480, respectively, as shown in the first data frame.  California produces the most milk and Alaska produces the least amount of milk as shown in data frames two and three.

```{r, echo=FALSE}

stat1996 <- milk1996 %>% summarise(average = mean(milk_million), med_1996= median(milk_million), max_produced = max(milk_million), min_produced = min(milk_million))

stat1996

max1996 <- milk1996 %>% top_n(1,milk_million)
max1996
min1996 <- milk1996 %>% top_n(-1,milk_million)
min1996

```
****
#### Ryan's Data
****
```{r, echo=FALSE}

milk1997 <- milk %>% filter(year == 1997) 
ggplot(data = milk1997 , mapping = aes(x = milk_million ))+
  geom_density()+
  ggtitle('Distribution of Milk Production in 1997')+
  xlab('Milk Produced(Millions lbs.)')+
  ylab('Density')
```

* The mean and median millions of pounds of milk are 3121.82 and 1436, respectively, as shown in the first data frame.  California produces the most milk and Alaska produces the least amount of milk as shown in data frames two and three.

```{r,echo=FALSE}

stat1997 <- milk1997 %>% summarise(average = mean(milk_million), med_1997= median(milk_million), max_produced = max(milk_million), min_produced = min(milk_million))

stat1997

max1997 <- milk1997 %>% top_n(1,milk_million)
max1997
min1997 <- milk1997 %>% top_n(-1,milk_million)
min1997

```
****
#### Anderson's Data
****
```{r, echo=FALSE}

milk1998 <- milk %>% filter(year == 1998) 
ggplot(data = milk1998, mapping = aes(x = milk_million )) +
  geom_density() + 
  ggtitle('Estimation of milk produced in 1998') +
  xlab('Milk Produced') +
  ylab('Density')

```

* The mean and median millions of pounds of milk are 3145.22 and 1411.5, respectively, as shown in the first data frame.  California produces the most milk and Alaska produces the least amount of milk as shown in data frames two and three.

```{r, echo=FALSE}
stat1998 <- milk1998 %>% summarise(average = mean(milk_million), med_1998= median(milk_million), max_produced = max(milk_million), min_produced = min(milk_million))

stat1998

max1998 <- milk1998 %>% top_n(1,milk_million)
max1998
min1998 <- milk1998 %>% top_n(-1,milk_million)
min1998


```


```{r, echo=FALSE}
milk_production1998 <- milk1998 %>%
  group_by(state) %>%
  summarize(average = mean(milk_million), med_1998= median(milk_million), max_produced = max(milk_million), min_produced = (milk_million)) %>%
  as_tibble()
  
```
****
#### Ethan's Data
****
```{r, echo=FALSE}
milk1999 <- milk %>% filter(year == 1999) 
ggplot(data = milk1999 , mapping = aes(x = milk_million ))+
  geom_density()+
  ggtitle('Distribution of Milk Production in 1999')+
  xlab('Milk Produced(Millions lbs.)')+
  ylab('Density')
```

* The mean and median millions of pounds of milk are 3251.8 and 1418, respectively, as shown in the first data frame.  California produces the most milk and Alaska produces the least amount of milk as shown in data frames two and three.

```{r, echo=FALSE}

stat1999 <- milk1999 %>% summarise(average = mean(milk_million), med_1999= median(milk_million), max_produced = max(milk_million), min_produced = min(milk_million))

stat1999

max1999 <- milk1999 %>% top_n(1,milk_million)
max1999
min1999 <- milk1999 %>% top_n(-1,milk_million)
min1999

```
****
#### David's Data
****

```{r, echo=FALSE}

milk2000 <- milk %>% filter(year == 2000) 
ggplot(data = milk2000 , mapping = aes(x = milk_million ))+
  geom_density()+
  ggtitle('Distribution of Milk Production in 2000')+
  xlab('Milk Produced(Millions lbs.)')+
  ylab('Density')
```

* The mean and median millions of pounds of milk are 3347.84 and 1453.5, respectively, as shown in the first data frame.  California produces the most milk and Alaska produces the least amount of milk as shown in data frames two and three.

```{r, echo=FALSE}
stat2000 <- milk2000 %>% summarise(average = mean(milk_million), med_2000= median(milk_million), max_produced = max(milk_million), min_produced = min(milk_million))

stat2000

max2000 <- milk2000 %>% top_n(1,milk_million)
max2000
min2000 <- milk2000 %>% top_n(-1,milk_million)
min2000

```

